### 2025-06-20 modern-portfolio-theory.qmd
20250620 - remove covariance matrix b/c too big

Here is the variance-covariance matrix of players' performance (it is very large because there are many players):

```{r}
dataForVarCovMatrix <- player_stats_weekly_recent %>% 
  select(player_id, week, fantasyPoints) %>% 
  pivot_wider(
    names_from = player_id,
    values_from = fantasyPoints
  )

>>>>

Here is the code to generate the variance-covariance matrix of players' performance (it is very large because there are many players):

```{r}
dataForVarCovMatrix <- player_stats_weekly_recent %>% 
  select(player_id, week, fantasyPoints) %>% 
  pivot_wider(
    names_from = player_id,
    values_from = fantasyPoints
  )
```
